---
title: "Class Survey"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    vertical_layout: scroll
    logo: includes/nav_logo.svg
    favicon: includes/favicon.ico
---

<style type="text/css">

.chart-title {  /* chart_title  */
   font-size: 30px;
   font-family: Algerian;

</style>

```{r include = FALSE}

## INIT ================================
library(DT)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(knitr)
library(plotly)


## LOAD DATA ===========================
load("data/survey.rda")


## Local Vars ==========================
brks <- c(0, 25, 50, 75, 100)
set.seed(12)
colors <- c("#872634","#363636","goldenrod","#007574","#762A83",
            "#05C3DE","#E5E4E0","#CF8D7C","#5F1E5E","lightblue4")

```
# Raw Data

### The Raw Data

```{r echo = FALSE, results = "asis"}

datatable(survey)

```

# Demographics

## Col1

### Age

```{r echo = FALSE}

cols <- colors[1:1]

plt <-
    ggplot(survey, aes(x = as.numeric(age))) +
    geom_histogram(aes(y = 100*..density..), fill = cols) +
    geom_density(aes(y = (100.0*..density..))) +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    labs(x = "Age", y = "Percent") +
    theme(axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

### Gender

```{r echo = FALSE}

if (length(unique(survey$gender)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$gender))]
} else {
    cols <- sample(colors, length(unique(survey$gender)), replace = TRUE)
}
    
plt <-
    ggplot(survey, aes(x = gender, fill = gender)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=cols) +
    labs(x = "Gender", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

### Home State

```{r echo = FALSE}

if (length(unique(survey$home_state)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$home_state))]
} else {
    cols <- sample(colors, length(unique(survey$home_state)), replace = TRUE)
}

plt <-
    ggplot(survey, aes(x = home_state, fill = home_state)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=colors) +
    labs(x = "Home State", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

# Educationally Speaking

### Year In School

```{r echo = FALSE}

if (length(unique(survey$school_year)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$school_year))]
} else {
    cols <- sample(colors, length(unique(survey$school_year)), replace = TRUE)
}

plt <-
    ggplot(survey, aes(x = school_year, fill = school_year)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=colors) +
    labs(x = "Year In School", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

### Degree

```{r echo = FALSE}

if (length(unique(survey$degree)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$degree))]
} else {
    cols <- sample(colors, length(unique(survey$degree)), replace = TRUE)
}

plt <-
    ggplot(survey, aes(x = degree, fill = degree)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=colors) +
    labs(x = "Degree", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

### Career

```{r echo = FALSE}

if (length(unique(survey$career)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$career))]
} else {
    cols <- sample(colors, length(unique(survey$career)), replace = TRUE)
}

plt <-
    ggplot(survey, aes(x = career, fill = career)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=colors) +
    labs(x = "Career", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

# Experience With Data

### Do you like Math?

```{r echo = FALSE}

if (length(unique(survey$like_math)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$like_math))]
} else {
    cols <- sample(colors, length(unique(survey$like_math)), replace = TRUE)
}

plt <-
    ggplot(survey, aes(x = like_math, fill = like_math)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=colors) +
    labs(x = "Like Math", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

### Are you good at counting things?

```{r echo = FALSE}

if (length(unique(survey$good_counter)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$good_counter))]
} else {
    cols <- sample(colors, length(unique(survey$good_counter)), replace = TRUE)
}

plt <-
    ggplot(survey, aes(x = good_counter, fill = good_counter)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=colors) +
    labs(x = "Good Counter", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

### What is (5+1)/2?

```{r echo = FALSE}

if (length(unique(survey$algebra_quiz)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$algebra_quiz))]
} else {
    cols <- sample(colors, length(unique(survey$algebra_quiz)), replace = TRUE)
}

plt <-
    ggplot(survey, aes(x = algebra_quiz, fill = algebra_quiz)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=colors) +
    labs(x = "Algebra Quiz", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

### Have you ever analyzed data?

```{r echo = FALSE}

if (length(unique(survey$ever_analyzed)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$ever_analyzed))]
} else {
    cols <- sample(colors, length(unique(survey$ever_analyzed)), replace = TRUE)
}

plt <-
    ggplot(survey, aes(x = ever_analyzed, fill = ever_analyzed)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=colors) +
    labs(x = "Ever Analyzed", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

### Data Analysis Tools

```{r echo = FALSE}

tmp <- data.frame(table(tools$ans))
names(tmp) <- c("Tools", "Count")
cols <- sample(colors, 16, replace = TRUE)

plt <-
    ggplot(tmp, aes(x = Tools, y = Count)) +
    geom_bar(stat = "identity", fill = "#872634") +
##geom_density() +
scale_y_continuous(limits = c(0,max(tmp$Count))) +
    labs(x = "Tools", y = "Count") +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 90, hjust = 1, size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols); rm(tmp)


```

# Inquiring Minds Want To Know

### Who do you think will win the next World Series?

```{r echo = FALSE}

if (length(unique(survey$world_series)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$world_series))]
} else {
    cols <- sample(colors, length(unique(survey$world_series)), replace = TRUE)
}

plt <-
    ggplot(survey, aes(x = world_series, fill = world_series)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=colors) +
    labs(x = "World Series", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))


ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

### Are you wondering why I am asking you these questions?

```{r echo = FALSE}

if (length(unique(survey$why_questions)) <= length(colors)) {
    cols <- colors[1:length(unique(survey$why_questions))]
} else {
    cols <- sample(colors, length(unique(survey$why_questions)), replace = TRUE)
}

plt <-
    ggplot(survey, aes(x = why_questions, fill = why_questions)) +
    geom_bar(aes(y = 100.0*(..count..)/sum(..count..))) +
    ##geom_density() +
    scale_y_continuous(limits = c(0,100), breaks = brks, labels = brks) +
    scale_fill_discrete(drop = FALSE) +
    scale_x_discrete(drop = FALSE) +
    scale_fill_manual(values=colors) +
    labs(x = "Why Questions", y = "Percent") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=20),
          axis.text.y = element_text(size=20),  
          axis.title.x = element_text(size=25, face = "bold"),
          axis.title.y = element_text(size=25, face = "bold"))

ggplotly(plt)

rm(tmp); rm(plt); rm(cols)

```

# Discussion

## Col1

### Quotable Quote:

    Mathematics is the language in which God has written the universe.
    
    -- Galileo Galilei

***

This is not a statistics course. It is an analysis course.

## Col2

### Course Goals:

Teach you how to:

- Develop and answer research questions.
- Download, manage, and characterize data.
- Use data to tell a compelling story.

### Three Maxims:

1. Counting is hard.
2. If you are doing it manually - you are doing it wrongly.
3. If a marmot cannot understand your writing, neither can most
   humans. 


### Some things to ponder:

- Did you learn anything about the people taking this class (as a group)?
- Did you learn anything about what we will be doing this semester?
- Did you see any pie charts?
- Would you like to see how I did this?
